Presentation Title

### 2017-03-15 chapters/ch2-checkpoint.tex
Presentation background section

\item A block of type $\gamma$ is a five-tuple, i.e.
  $$c_{i,j} = (\texttt{h}(b_{i,j}), H(\mathcal{C}_r), r, p, s)$$
  where $\mathcal{C}_r$ is the consensus result in round $r$ and $p \in {0,1}$
  which indicates whether $i$ wish to become a promoter in the following
  consensus round, finally $s$ is a signature of the block.

>>>>

\item A block of type $\gamma$ is a five-tuple, i.e.
  $$c_{i,j} = (\texttt{h}(b_{i,j-1}), \texttt{h}(\mathcal{C}_r), r, p, s)$$
  where $\mathcal{C}_r$ is the consensus result in round $r$ and $p \in {0,1}$
  which indicates whether $i$ wish to become a promoter in the following
  consensus round, finally $s$ is a signature of the block.
